\bfseries\LARGE\singlespacing{Spatiotemporal risks of \emph{Mycobacterium tuberculosis} transmission: A modelling study of environmental, clinical, and patient movement data}

### 2024-03-04 doc/paper/manuscript.tex

...

>>>>

\begin{figure}
    \centering
    \includegraphics{results/data/co2-levels-over-time.png}
    \includegraphics{results/data/air-changes-per-hour.png}
     \includegraphics{results/data/no-people-spatial.png}
    \includegraphics{results/data/no-people-over-time.png}
    \includegraphics{results/data/time-in-clinic.png}
    \includegraphics{results/data/number-close-contacts.png}
    \includegraphics{results/data/time-close-contacts.png}
    \caption{\textbf{Environmental conditions and patient movement characteristics.} \textbf{(a)}~CO$_2$ levels per room of the clinic over time per day. \textbf{(b)}~Air change rates per room of the clinic. \textbf{(c)}~Total number of tracks recorded per unit space in the clinic over the study period. \textbf{(d)}~Number of people in the clinic over time per day. \textbf{(e)}~Time spent in the clinic per clinical attendee. \textbf{(f)}~Density distribution of the number of close contacts per clinical attendee during their visit. \textbf{(g)}~Density distribution of the time spent in close contact per clinical attendee during their visit.}
    \label{fig:input-data-descriptives}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{results/modeling/main-figure.png}
    \caption{\textbf{Spatiotemporal modeling results.} \textbf{(a)}~Average quanta concentration in the morning and afternoon in the clinic. \textbf{(b)}~Mean and median risk of infection per clinical attendee. Low: <5\%, Medium: 5-10\%, High: >10\%. \textbf{(c)}~Association of mean infection risk with patient movement characteristics and environmental conditions. }
    \label{fig:main-modeling-results}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{results/modeling/mean-roi-comparison.png}
    \caption{\textbf{Scenario modeling results.} Mean risk of infection per clinical attendee if \textbf{(a)}~masks had not been worn by all clinical attendees and staff, \textbf{(b)}~the ventilation rate had been lower as in the year before the COVID-19 pandemic, \textbf{(c)}~the number of infectious people in the clinic corresponded to the prevalence of TB in the population, or \textbf{(d)}~the number of infectious people in the clinic corresponded to the number of diagnosed TB patients and those suspected of TB due to respiratory symptoms when attending the clinic. Low: <5\%, Medium: 5-10\%, High: >10\%.}
    \label{fig:scenario-results}
\end{figure}
